---
title: DSC 520 Week 9 Exercise
subtitle: ANOVA Regression
---

<!-- Comments
1. figure out how to create either R chunk snippets for quick shortcut copy and paste or
2. latex-like preambles for setup configuration for installing packages and loading libraries
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

packages <- c(
	"tidyverse",
	"ggplot2",
	"car",
	"dplyr",
	"welchADF"
)

for (package in packages) {
  if (!requireNamespace(package, quietly = TRUE))
    install.packages(package)
}

lapply(packages, library, character.only=TRUE)

```

**Week 9 Exercise**
Using the travel insurance dataset from the prior week, 
1. Create one-way ANOVA.
2. Create two-way ANOVA. 
3. Use AIC to determine which one is better for the dataset.


```{r}
# Import dataset
df <- read.csv("travel_insurance.csv")

# Rename and create data frame with columns of interest
df <- df %>%
  rename(Amount = Commision..in.value.) %>%
  select(Duration, Net.Sales, Amount,Agency.Type,Agency)

# Store column names as variables in global environment
d.vectorize <- function(x,y) {
  list2env(setNames(lapply(x, function(col) na.omit(y[[col]])),x), envir= .GlobalEnv)
}



# Task 1: Create One-way ANOVA

df$Agency.Type <- as.factor(df$Agency.Type)
df$Agency <- as.factor(df$Agency)

columns <- c("Duration","Net.Sales","Amount","Agency.Type","Agency")
d.vectorize(columns,df)

# with(df, leveneTest(Net.Sales,Agency.Type))
# with(df, leveneTest(Amount,Agency.Type))
# with(df, leveneTest(Net.Sales,Agency))
# with(df, leveneTest(Amount,Agency))

oneway.amount <- lm(Amount ~ Agency.Type, data = df)
oneway.sales <- lm(Net.Sales ~ Agency.Type, data = df)

# two-way ANOVA

res1 <- lm(Amount ~ Agency * Agency.Type, data=df) # two-way
res2 <- lm(Net.Sales ~ Agency * Agency.Type, data=df)

twoway.amount <- lm(res1,data=df)
twoway.sales <- lm(res2,data=df)
twoway.amount
twoway.sales
summary(twoway.amount)
summary(twoway.sales)

# Question 3: AIC

AIC.amount <- AIC(oneway.amount,twoway.amount)
AIC.sales <- AIC(oneway.sales,twoway.sales)
AIC.amount
AIC.sales
summary(AIC.amount)
summary(AIC.sales)

```

One-way ANOVA using Agency.Type as the predictor is improved by adding a second interacting predictor Agency and using two-way ANOVA for both Net.Sales and Commission Amount, as the AIC decreases in value with the addition of a second predictor into the model. Therefore, within this particular data set, two-way ANOVA is better than one-way ANOVA in predicting independent variables (Net.Sales and Amount) with the use of dependent variables (Agency.Type and Agency) as predictors.


```
