---
title: DSC 520 Week 8 Exercise 1
subtitle: Correlation
author: "Dong Woon Kim"
date: "2025-07-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r install packages}

packages <- c(
  "lsa",
  "pheatmap"
)

lapply(packages,install.packages, character.only = TRUE)
lapply(packages,library, character.only = TRUE)
```

```{r import dataset}
df <- read.csv("G:/My Drive/3. Informatyki (MSDS)/Data Science/R/dsc_520_week_8_correlation_confidence_intervals/travel_insurance.csv")
View(df)
```


Compute the correlation coefficient between any two variables.

The correlation coefficient between Duration and Net Sales is 0.429.
The correlation coefficient between Duration and Commission is 0.345.
The correlation coefficient between Net Sales and Commission is 0.651.

```{r}
df <- read.csv("G:/My Drive/3. Informatyki (MSDS)/Data Science/R/dsc_520_week_8_correlation_confidence_intervals/travel_insurance.csv")
duration <- df$Duration
sales <- df$Net.Sales
df$Amount <- df$Commision..in.value. # not necessary but cleaner column header
amount <- df$Amount
View(df)

a <- duration
b <- sales
c <- amount

r_ab <- cor(a,b)
r_ac <- cor(a,c)
r_bc <- cor(b,c)

r_ab
r_ac
r_bc
```

Compute the Pearson, Spearman, and Kendall correlations between any two variables.

```{r}
# Pearson correlation coefficient
r_ab.p <- cor(a,b, method="pearson")
r_ac.p <- cor(a,c, method="pearson")
r_bc.p <- cor(b,c, method="pearson")

# Spearman correlation coefficient
r_ab.s <- cor(a,b, method="spearman")
r_ac.s <- cor(a,c, method="spearman")
r_bc.s <- cor(b,c, method="spearman")

# Kendall correlation coefficient
r_ab.k <- cor(a,b, method="kendall")
# r_ac.k <- cor(a,c, method="kendall")
r_bc.k <- cor(b,c, method="kendall")
```

Create a correlation matrix for all variables.

```{r}
data <- data.frame(a,b,c)
cor.matrix <- cor(data)
print(cor.matrix)
```

Compute the covariance between any two variables.

The covariance between Duration and Net Sales is 2134.2.
The covariance between Duration and Commission is 695.0.
The covariance between Net Sales and Commission is 630.1.


```{r}

cov(a,b)
cov(a,c)
cov(b,c)

```

Compute the Cosine Similarity between the same two variables as you use for #2. Plot the two together.


```{r}

data.matrix <- cbind(a,b,c)
dm.cos <- cosine(data.matrix)
colnames(dm.cos) <- c("Duration", "Net Sales", "Commission")
pheatmap(dm.cos,
         main = "",
         display_numbers = TRUE)
# ?pheatmap()

```

