---
title: "DSC_520_week_3_exercise"
author: "Dong Woon Kim"
date: "2025-06-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Week 3 Exercise

## 1. Show the distributions of values visually. Explain, in comments, what those distributions mean statistically. Be thorough.

```{r}
sales <- read.csv("~/R/sales_data_sample.csv")

# Load data frames

df.quantity <- sales$Quantity
df.price <- sales$UnitPrice
df.sales <- sales$TotalSales

# Calculate means

mean.quantity <- mean(df.quantity)
mean.price <- mean(df.price)
mean.sales <- mean(df.sales)

# Calculate standard deviations

sd.quantity <- sd(df.quantity)
sd.price <- sd(df.price)
sd.sales <- sd(df.sales)

# Plot normal distribution curve of Total Sales column values

x <- seq(min(df.sales), max(df.sales), length=100)
y <- dnorm(x, mean=mean.sales, sd=sd.sales)
plot(x, y, type="l",lwd=1)
lines(x, y, col="blue", lwd = 1)

# Another way to do the same thing

hist(df.sales, prob=TRUE, main = "Total Sales", xlab = "Total Sales", ylab = "Density")
lines(density(df.sales), col="red")

# Comments: the distribution curves show that the values are left skewed, meaning that most of the values fall below the mean of the distribution of values (to the left of the mean). Left- or right-skewed distribution curves suggest that the distribution of values is not normal, and thus is non-parametric. Therefore, if this were a sample set of data to be used for statistical testing, non-parametric statistical tests must be used for statistical testing.
```
  
# 2. Show the values of central tendency, both numerically and visually. 

## Unit Price Analysis

```{r}

# Plot normal distribution curve of Unit Price column values

x <- seq(min(df.price), max(df.price), length=100)
y <- dnorm(x, mean=mean.price, sd=sd.price)
plot(x, y, type="l",lwd=1)
lines(x, y, col="blue", lwd = 1)

# Another way to do the same thing

hist(df.price, prob=TRUE, main = "Unit Price", xlab = "Price", ylab = "Density")
lines(density(df.price), col="red")

summary(df.price)
mean.price
sd.price
```

## Quantity Analysis

```{r}
# Plot normal distribution curve of Quantity column values

x <- seq(min(df.quantity), max(df.quantity), length=100)
y <- dnorm(x, mean=mean.quantity, sd=sd.quantity)
plot(x, y, type="l",lwd=1)
lines(x, y, col="blue", lwd = 1)

# Another way to do the same thing

hist(df.quantity, prob=TRUE, main = "Total Sales", xlab = "Total Sales", ylab = "Density")
lines(density(df.quantity), col="red")

summary(df.quantity)
mean.quantity
sd.quantity

summary(df.sales)
sd(df.sales)
```

## 3. Interpret those values in your own words in Markdown.

The mean total sales value is $409.05 with a standard deviation of $402.01. 

The mean unit price is $52.41 with a standard deviation of $28.69, with a bi-modal distribution around the sample mean. This means that the distribution of unit price values may not be normally distributed.

The mean quantity of products order with each individual order is 9.59 with a standard deviation of 5.66. The distribution of values is centered around the mean without skew and bi-modal peaks, resembling a normally distribution curve. 
  
  
## 4. Show the measures of dispersion, visually and numerically (where appropriate). Interpret those values in Markdown.

```{r}
df.price
summary.price <- summary(df.price)
summary.price
range.price <- max(df.price) - min(df.price)
range.price
var.price = sd.price^2
var.price
iqr.price = summary.price[5] - summary.price[2]
iqr.price

df.sales
range.sales <- max(df.sales) - min(df.sales)
range.sales
var.sales = sd.sales^2
var.sales
iqr.sales = summary.sales[5] - summary.sales[2]
iqr.sales


df.quantity
range.quantity <- max(df.quantity) - min(df.quantity)
range.quantity
var.quantity = sd.quantity^2
var.quantity
iqr.quantity = summary.quantity[5] - summary.quantity[2]
iqr.quantity
```
The ranges (max-min) for unit price, total sales, and quantity are 143.1, 1886.52, and 18, respectively. The variances are 823.24, 16108.2, and 32.09. 

## 5. Visually depict the Interquartile range. Interpret the IQR for the dataset (in Markdown).

```{r}

box.price <- boxplot(df.price, ylab = "Price ($)")
box.sales <- boxplot(df.sales, ylab = "Total Sales")
box.quantity <- boxplot(df.quantity, ylab = "Quantity")

box.price
box.sales
box.quantity
```


## 6. Create the statistics moments for the dataset. 

```{r}

# custom function to approximate skewness

skew <- function(df) {
  x <- mean(df)
  y <- median(df)
  z <- sd(df)
  skew <- 3*(x-y)/z
  return(skew)
}

# custom function to calculate kurtosis

kurtosis <- function(df) {
  x <- mean(df)
  y <- length(df)
  z <- sd(df)
  
  kurtosis = (sum((df-x)^4)/y)/(z^4)
  return(kurtosis)
}


# Total sales statistics moments

mean.sales
var.sales
skew.sales <- skew(df.sales)
skew.sales
kurtosis.sales <- kurtosis(df.sales)
kurtosis.sales

# Unit price statistics moments

mean.price
var.price
skew.price <- skew(df.price)
skew.price
kurtosis.price <- kurtosis(df.price)
kurtosis.price

# Quantity statistics moments

mean.quantity
var.quantity
skew.quantity <- skew(df.quantity)
skew.quantity
kurtosis.quantity <- kurtosis(df.quantity)
kurtosis.quantity

```
## 7. Experiment with histogram binning for the categorical data in R. This is open-ended intentionally because this dataset isn’t ideal for binning, but I want you to build something using binning just to see how it works.