---
title: "Week 4 Exercise"
author: "Dong Woon Kim"
date: "2025-06-29"
output: 
  html_document:
    code_folding: show
    results: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results='hide')
```

<!-- install and load packages -->
```{r install packages, echo=TRUE, include=FALSE, results='hide'}
setwd("~/R")
packages <- c("rmarkdown", "readr")
lapply(packages,library, character.only = TRUE)

```

**Using this dataset, perform the following transformations:**

- [x] Scale the numerical data.**
- [x] Fix any skew as best you can.**
- [x] Normalize any columns not normalized using any of the available techniques (don’t use the same technique twice).
- [ ] Using data simulation, fill in the missing values for the release_date variable (not the others).
- [x] Be sure to thoroughly document your logic (why you’re doing things) and commentary (e.g., your view of the results) using Markdown.

<!-- transformations:

- [x] A. z-scoring
- [x] B. min-max scaling
- [x] C. log
- [x] D. square-rooting
- [x] E. Fisher-z
- [ ] tiedrank

-->

<!-- custom functions:

I. d.vectorize
II. d.lapply

-->

<!-- 

apparently the de facto way to turn any non-Gaussian distribution to one that is Gaussian is to:

1. rank-transform, then
2. min-max scale, then
3. Fisher-z transform

idk if true, but let's try.

--> 


```{r}

# import and load dataset
df <- read.csv("./week_4.csv")
columns <- c("critic_score", "total_sales", "na_sales", "jp_sales", "pal_sales", "other_sales")

# I. d.vectorize
# custom function to extract and vectorize columns of interest and load them as variables into the global environment according to their column names, where:
# x = columns
# y = df

d.vectorize <- function(x,y) {
  list2env(setNames(lapply(x, function(col) na.omit(y[[col]])),x), envir= .GlobalEnv)
}

d.vectorize(columns,df)

# II. d.lapply
# custom function to run a function across a list of data frames with one line of code, where:
# x = columns
# y = function
# z = prefix

d.lapply <- function(x,y,z) {
  for (name in x) {
    vec <- get(name, envir = .GlobalEnv)
    vec.trans <- y(vec)
    assign(paste0(z,name), vec.trans, envir = .GlobalEnv)
    }
}

# III. d.zscore
# custom function for z-scoring around the mean where:
# x = df
# y = column_name

d.zscore <- function(x) {
  mean.x <- mean(x, na.rm = TRUE)
  sd.x <- sd(x, na.rm = TRUE)
  z.x <- (x - mean.x)/sd.x
  return(z.x)
}


# III. d.minmax
# min-max scaling, where:
# x = df
# a = lower limit (default = 0)
# b = upper limit (default = 1)

d.minmax <- function(x, a=0,b=1) {
  min.x <- min(x)
  max.x <- max(x)
  range.x <- max.x - min.x
  minmax.x <- (x - min.x)/range.x 
  scale <- (b - a) + a
  minmax.x.s <-  minmax.x * scale
  
  return(minmax.x.s)
}

# IV. Fisher-z (practically just a name change)
d.Fisherz <- function(x) {
  x.Fisherz <- atanh(x)

  return(x.Fisherz)
}

d.lapply(columns,log,"log." )
d.lapply(columns,d.zscore,"z.")
d.lapply(columns,d.minmax,"minmax.")
d.lapply(columns,rank,"rank.")
d.lapply(columns,sqrt,"sqrt.")
transf.critic_scores <- d.Fisherz(d.minmax(rank(critic_score),-0.999,0.999))
transf.total_sales <- d.Fisherz(d.minmax(rank(total_sales),-0.999,0.999))
transf.na_sales <- d.Fisherz(d.minmax(rank(na_sales),-0.999,0.999))
transf.jp_sales <- d.Fisherz(d.minmax(rank(jp_sales),-0.999,0.999))
transf.pal_sales <- d.Fisherz(d.minmax(rank(pal_sales),-0.999,0.999))
transf.other_sales <- d.Fisherz(d.minmax(rank(other_sales),-0.999,0.999))

d.skew <- function(df) {
  x <- mean(df, na.rm=TRUE)
  y <- median(df, na.rm=TRUE)
  z <- sd(df, na.rm=TRUE)
  skew <- 3*(x-y)/z
  return(skew)
}

# skewness and transformations 

# critic score
d.skew(critic_score)
d.skew(z.critic_score)
d.skew(minmax.critic_score)
d.skew(rank.critic_score)
d.skew(sqrt.critic_score)
d.skew(transf.critic_scores)

# total sales
d.skew(total_sales)
d.skew(z.total_sales)  
d.skew(transf.total_sales)

# na sales
d.skew(na_sales)
d.skew(z.na_sales)
d.skew(transf.na_sales)

# jp sales
d.skew(jp_sales)
d.skew(z.jp_sales)
d.skew(transf.jp_sales)

# pal sales
d.skew(pal_sales)
d.skew(z.pal_sales)
d.skew(transf.pal_sales)

# other sales
d.skew(z.other_sales)
d.skew(z.other_sales)
d.skew(transf.other_sales)

# note to professor: I don't know what I'm doing wrong here, I applied the transformations according to the course text book section 6.6.4 on page 224 but the skewness is not corrected and the histograms do not show a normally distributed curve. Can you please take a look and tell me either if something is wrong, or why a non-Gaussian to Gaussian set of transformations can result in skewed and non-normally distributed histogram?

```


